---
title: "BANC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BANC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{nat.nblast}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
have_fafbsegpy=!inherits(try(fafbseg:::check_fafbsegpy(), silent = TRUE), 'try-error')
```

```{r setup, message=FALSE}
library(fancr)
library(dplyr)
```


## Introduction 

The BANC is a female brain and nerve cord dataset imaged by Wei Lee's lab (Minsu Kim and Jasper Phelps). See its [wiki](https://github.com/jasper-tms/the-BANC-fly-connectome/wiki). 
Since the BANC infrastructure is most similar to FANC (the female adult nerve cord),
we have decided to use the fancr package to provide some basic functionality to
interact with the BANC dataset.

### with_banc and choose_banc

Like the underlying fafbseg package, fancr has a concept of an active segmentation.

You can now use `choose_banc` to set the active segmentation to BANC, which
should target most `fanc_` functions to use the BANC. Of course if you want to 
use a different dataset (fanc, flywire) you need to remember to switch back.

A potentially less intrusive approach uses `with_banc()` to temporarily switch
the default segmentation to the BANC, run your code, and then switch back again.
Just wrap `flywire_.*` or `fanc_.*` functions with this to target them at the BANC.


```{r}
# supervoxel id to root id
with_banc(fafbseg::flywire_rootid('76071705504180616'))
```


is this id up to date?

```{r}
with_banc(fafbseg::flywire_islatest('720575941472355131'))

```

Find up to date root id
```{r}
with_banc(fafbseg::flywire_latestid('720575941472355131'))
```

### CAVE tables

```{r}
cell_info=banc_cave_query('cell_info')
cell_info %>%
  filter(tag2=='anterior-posterior projection pattern') %>%
  count(tag)
```

Or we can just request a specific tag type

```{r}
nc=banc_cave_query('cell_info', 
                   filter_in_dict = list(tag2='anterior-posterior projection pattern'))
nrow(nc)
```


### L2 skeletons and dotprops

BANC is already set up with an L2 cache which can be used to get rapid neuron
skeletons.

```{r, eval=have_fafbsegpy}
n=with_banc(fanc_read_l2skel("720575941552483585"))
plot(n)
```

Similarly we can make "dotprops" objects suitable for NBLAST.

```{r, eval=have_fafbsegpy}
ids <- with_banc(flywire_rootid(c("76070056370827492", "76142074315307608", "76142074315367069")))
dps=with_banc(read_l2dp(ids))
plot(dps)
```

```{r, eval=have_fafbsegpy}
library(nat.nblast)
aba=nblast_allbyall(dps)
hc=nhclust(scoremat = aba)
plot(hc)
```

